SDR enhancement by clouds

### 2024-02-29 article/article.Rmd
Commit 2024-02-29 20:15

---
title:    SDR enhancement by clouds
subtitle: A Short Subtitle
author:
  - Athanasios N. Natsis^[Laboratory of Atmospheric Physics natsisphysicist@gmail.com] 
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
  - name:         Charikleia Meleti
    email:        meleti@auth.gr
    affiliation:  Laboratory of Atmospheric Physics
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2

@@

```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
knitr::include_graphics("../images/groups-6.png")
```

@@

-   max
-   seasonal
-   trends
-   duration
-   occurrence
-   SZA

>>>>

---
title:    SDR enhancement by clouds

subtitle: A Short Subtitle

author:
  - Athanasios N. Natsis^[Laboratory of Atmospheric Physics _natsisphysicist@gmail.com_] 
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics _abais@auth.gr_] 
  - Charikleia Meleti^[Laboratory of Atmospheric Physics _meleti@auth.gr_]

abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.

keywords: 
  - keyword1
  - keyword2

@@

@@

-   max value ECE
-   seasonal
-   trends
-   duration
-   occurrence
-   SZA
